### 2022-10-24 types.tex
another system overhaul, maybe with its own bugs.

    {\inferrule{A : in(dₐ), A : out(dₐ),… ;A : τₐ,…;.  ⊢ p : τ}
      {⊢ "declare"~A…~"in"~p : τ}}

    {
      \inferrule{\inputs(\op) = τ \\ 
        C;Γ;. ⊢ p : τ \\ C';Γ';d.p.\op[0] ⊢ p' : τ'}
                {{C,C'};Γ,Γ';{d} ⊢ [p]\op[p'] : τ'}}

    {\inferrule[relevant-parallel]
      {C₁;Γ_1;d[n] ⊢ p₁ : τ₁ \\ C₂;Γ_2;d[n+1] ⊢ p₂ : τ₂}
      {C₁,C₂;Γ_1,Γ_2;d[n] ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[general-parallel]
      {C₁;Γ_1;. ⊢ p₁ : τ₁ \\ C₂;Γ_2;. ⊢ p₂ : τ₂}
      {C₁,C₂;Γ_1,Γ_2; . ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[exchange-C]
      {C,C_2,C_1,C' ;Γ; d ⊢ p : τ}
      {C,C_1,C_2,C' ;Γ; d ⊢ p : τ}}

    {\inferrule[exchange-gamma]
      {C ;Γ,Γ_1,Γ_2,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_2,Γ_1,Γ'; d ⊢ p : τ}}

    {\inferrule[weaken-gamma]
      {C ;Γ,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_w,Γ'; d ⊢ p : τ}}

    {\inferrule[contract-gamma]
      {C ;Γ,Γ_c,Γ_c,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_c,Γ'; d ⊢ p : τ}}

    {\inferrule[unfold]{A:d',C;Γ;d[A/d] ⊢ p : τ}{A:d',C;Γ;d ⊢ p : τ}}

    {\inferrule[fold]{A:d',C;Γ;d⊢ p : τ}{A:d',C;Γ;d[A/d]⊢ p : τ}}

    {\inferrule[varref-out]{Γ ⊢ d : τ}{A:out(d);Γ;d ⊢ A : τ}}

    {\inferrule[varref-in]{}{A:in(d);A : τ; . ⊢ A : τ}}

    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ C;Γ;d' ⊢ p : τ}{C;Γ;d ⊢ p : τ}}

    \end{mathpar}\MPM{There's something fishy going on with varref-in; right now, you could use it and then immediately apply unfold to get a derivation which might not typecheck. We need to prove this is not actually a problem.}
    %\includegraphics{freehand-types}
  \label{fig:types}
  \caption{Types: top-level}
\end{figure}
\begin{figure}
\begin{mathpar}

@@

>>>>

    {\inferrule{A : in(dₐ'.dₐ''), A : out(dₐ.dₐ''),… ⊢ p
    \\ dₐ' ∈ \{A.dₐ'', dₐ.dₐ''\}
    \\ (A : τₐ,… ⊢ dₐ.dₐ'' : τₐ)…
    }
      {⊢ "declare"~A…~"in"~p}}

    {
      \inferrule[pivot]{|\outputs(\op)| = |p'| \\ 
        C ⊢ p : d \\ C';d.op[0] ⊢ p'}
                {{C,C'} ⊢ [p]\op[p']}}

    {
      \inferrule[inward]{C ⊢ p : d}
                {{C} ⊢ [p]\op : d.\op[0]}}

{
      \inferrule[outward]{|\outputs(\op)| = |p'| \\
        C;d.\op[0] ⊢ p'}
                {{C};d ⊢ \op[p']}}

    {\inferrule[out-parallel]
      {C₁;d[n] ⊢ p₁ \\ C₂;d[n+1] ⊢ p₂}
      {C₁,C₂;d[n] ⊢ (p₁ ∣ p₂)}}

    {\inferrule[in-parallel]
      {C₁ ⊢ p₁ : d₁ \\ C₂ ⊢ p₂ : d₂}
      {C₁,C₂ ⊢ (p₁ ∣ p₂) : (d₁ ∣ d₂)}}

    {\inferrule[varref-out]{}{A:out(d);d ⊢ A}}

    {\inferrule[varref-out-approx]{}{A:out(d'.d);B.d ⊢ A}}\textit{\MPM{Is this sound? Or can it allow the paths to vary too much? I feel like probably the latter....}}

    {\inferrule[varref-in]{}{A:in(d) ⊢ A : d}}

    \end{mathpar}
  \label{fig:types}
  \caption{Types: top-level}
\end{figure}
\begin{figure}
\begin{mathpar}
    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' : τ}{Γ ⊢ d : τ}}

@@

    {\inferrule[exchange-C-in]
      {C,C_2,C_1,C' ;Γ ⊢ p : d}
      {C,C_1,C_2,C' ;Γ ⊢ p : d}}

    {\inferrule[exchange-C-out]
      {C,C_2,C_1,C' ;Γ; d ⊢ p}
      {C,C_1,C_2,C' ;Γ; d ⊢ p}}

    {\inferrule[exchange-gamma]
      {Γ,Γ_1,Γ_2,Γ' ⊢ φ}
      {Γ,Γ_2,Γ_1,Γ' ⊢ φ}}

    {\inferrule[weaken-gamma]
      {Γ,Γ'  ⊢ φ}
      {Γ,Γ_w,Γ' ⊢ φ}}

    {\inferrule[contract-gamma]
      {Γ,Γ_c,Γ_c,Γ' ⊢ φ}
      {Γ,Γ_c,Γ' ⊢ φ}}

\end{mathpar}    
    \caption{Types: boring structural stuff }
    \label{fig:types-structural}
\end{figure}
